Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
hi

All models fitted to the data in this investigation were nested and evaluations were based on information criteria including Akaike Information Criteria (AIC) and Bayesian Information Criteria (BIC). Additionally, we also used performance measures including the mean squared error (MSE), r-squared, and adjusted r-squared. The likelihood ratio test (LRT) was used in competing model comparisons testing the null hypothesis that the nested models are equivalent, and the extra parameters in the larger model do not improve the fit significantly, that is, these terms have effect sizes equivalent to 0. \@ref(tab:tabmodel) summarizes the model performance metrics compared for all models implemented in this investigation.

@@

Table \@ref(tab:tabmodel) summarizes the performance metrics across the
different models fitted to the data in our investigation.

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & df & AIC & BIC & MSE & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 41 & 15888.38 & 16117.55 & 173.69 & 0.36 & 0.34\\
Model 7 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```
```{r tabmodel, eval=FALSE, echo=FALSE}
## Model performance
tabmodel <- model.checks %>% 
  kable(format = "latex", caption = "Summary model performance measures.", digits = 2, booktabs = TRUE, col.names = c("df", "AIC", "BIC", "MSE", "R^2", "Adjusted R2"), escape = FALSE) %>% 
  add_footnote(label = c("df = degrees of freedom", "AIC = Akaike Information Criteria", "BIC = Bayesian Information Criteria", "MSE = Mean Squared Error"))
tabmodel
```

@@

# Conclussion

>>>>

All models fitted to the data in this investigation were nested and
evaluations were based on information criteria including Akaike
Information Criteria (AIC) and Bayesian Information Criteria (BIC). The
BIC is favored over the AIC due to its increasing penalty with larger
sample sizes, resulting in more stringent significance levels [@BIC].
Additionally, we also used performance measures including the mean
squared error (MSE), r-squared, and adjusted r-squared. The likelihood
ratio test (LRT) was used in competing model comparisons testing the
null hypothesis that the nested models are equivalent, and the extra
parameters in the larger model do not improve the fit significantly,
that is, these terms have effect sizes equivalent to 0.
\@ref(tab:tabmodel) summarizes the model performance metrics compared
for all models implemented in this investigation.

@@

Table \@ref(tab:tabmodel) presents an overview of various models applied
to our dataset. Model 6, utilizing best subset selection, reveals
notably high MSE, suggesting limited predictive efficacy. Models 1 and
2, not including variable selection techniques, highlight the impact of
incorporating the age-cholesterol interaction term, showing a reduction
in MSE. Models 3, 4, and 5 included solely significant univariate
regression variables. Model 5, with the lowest AIC and second lowest
BIC, demonstrates an acceptable MSE. Model 4, with the lowest MSE and
highest \$R\^2\$, implies predictive power, although its extensive terms
raise concerns of potential overfitting. Model 3, based solely on
significant univariate covariates, performs well but exhibits a higher
MSE than Models 4 and 5, suggesting the probable influence of
interaction terms. Models 7 and 8, employing LASSO, exhibit comparable
performance metrics, with Model 8 displaying reduced BIC and MSE,
attributed chiefly to the significant inclusion of an Age-Cholesterol
interaction term.

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & $\text{df}^a$ & $\text{AIC}^b$ & $\text{BIC}^c$ & $\text{MSE}^d$ & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
Model 7 & 41 & 15888.38 & 16117.55 & 173.69  & 0.36 & 0.34\\
Model 8 & 42 & 15849.19 & 16083.94 & 170.11  & 0.37 & 0.36\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```
```{r tabmodel, eval=FALSE, echo=FALSE}
## Model performance
tabmodel <- model.checks %>% 
  kable(format = "latex", caption = "Summary model performance measures.", digits = 2, booktabs = TRUE, col.names = c("df", "AIC", "BIC", "MSE", "R^2", "Adjusted R2"), escape = FALSE) %>% 
  add_footnote(label = c("df = degrees of freedom", "AIC = Akaike Information Criteria", "BIC = Bayesian Information Criteria", "MSE = Mean Squared Error"))
tabmodel
```

@@

# Conclusion
